---
title: "p8105_hw6_ts3349"
author: "Tessa Senders"
date: "12/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import libraries}
library(tidyverse)
library(broom)
library(p8105.datasets)
library(purrr)
library(modelr)
```


## Problem 1


```{r read in data prob 1}
homicide_df =
  read_csv("./data/homicide-data.csv", na = c("", "NA", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
    disposition == "Closed without arrest" ~ 0,
    disposition == "Open/No arrest" ~ 0,
    disposition == "Closed by arrest" ~ 1)
  ) %>%
  filter(victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>%
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


```{r prob 1 part 2}
baltimore_df =
  homicide_df %>%
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, data = baltimore_df, family = binomial()) %>% broom::tidy() %>%
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate -1.96 * std.error),
         CI_upper = exp(estimate + 1.96 * std.error)) %>%
  select(term, OR, starts_with("CI")) %>%
  knitr::kable(digits = 3)
```


```{r prob 1 part 3}
models_results_df = 
  homicide_df %>%
  nest(data = -city_state) %>%
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy) 
  ) %>%
    select(city_state, results) %>%
  unnest(results) %>%
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate -1.96 * std.error),
         CI_upper = exp(estimate + 1.96 * std.error)) %>%
  select(city_state, term, OR, starts_with("CI"))
```


```{r prob 1 part 4}
models_results_df %>%
  filter(term == "victim_sexMale") %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text = element_text(angle = 270, vjust = 0.5, hjust = 1)) +
  labs(
    title = "Confidence Intervals for The Odds Ratios of \n Unsolved Homicides by Sex in Various Cities",
    x = "City and State",
    y = "Odds Ratio(OR)",
    caption = "Data from the Washington Post GitHub")
```

Most of the odds ratios are less than 1, indicating that the outcome (resolution, i.e. closed with an arrest) is often less likely for male homicide victims than for female homicide victims.


## Problem 2


```{r load and tidy data}
birthweight_df <- read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(babysex = as_factor(babysex),
         frace = as_factor(frace),
         malform = as_factor(malform),
         mrace = as_factor(mrace))

birthweight_df %>% 
  map(~sum(is.na(.)))
```


```{r prob 2, 2 given models}
set.seed(1)
fit_1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
fit_2 = lm(bwt ~ bhead * blength * babysex, data = birthweight_df)

cv_df =
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    simple_model = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interaction_model = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
    #my_model = map() 
  ) %>%
    
  mutate(
    rmse_simple = map2_dbl(simple_model, test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(interaction_model, test, ~rmse(model = .x, data = .y)),
    #rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x, data = .y))
    )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```


One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate


## Problem 3


```{r prob 3 load data}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r prob 3 draw samples}
set.seed(1)

boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

boot_straps = 
  data_frame(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )


bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance),  
    results_2 = map(models, broom::tidy)) %>%
  select(-strap_sample, -models) %>% 
  unnest(results,
         results_2) %>% 
  select(strap_number, r.squared, term, estimate) %>%
  pivot_wider(names_from = term,
              values_from = estimate) %>%
  janitor::clean_names() %>%
  mutate(log_value = log(intercept * tmin))

bootstrap_results
```


```{r prob 3 plots}
bootstrap_results %>% 
  ggplot(aes(x = tmin)) + 
  geom_density() + 
  labs(
    title = "5000 Boostrap Estimates of Minimum Temperature (C)",
    x = "Minimum Temperature (C)",
    y = "Density",
    caption = "Data from the New York NOAA weather stations"
  )

bootstrap_results %>%
  ggplot(aes(x = log_value)) + 
  geom_density()+ 
  labs(
    title = "5000 Boostrap Estimates of log(B_0_hat * B_1_hat)",
    x = "log(B_0_hat * B_1_hat)",
    y = "Density",
    caption = "Data from the New York NOAA weather stations"
  )
```


```{r problem 3 quantiles}
bootstrap_results %>% 
  summarize(
    ci_lower_tmin = quantile(tmin, 0.025), 
    ci_upper_tmin = quantile(tmin, 0.975),
    ci_lower_log = quantile(log_value, 0.025), 
    ci_upper_log = quantile(log_value, 0.975))
```

